Network Analysis of Code Similarity

### 2014-11-21 network-analysis.Rmd
Isolate subgraphs

>>>>

Get just the component graphs

```{r}
sub <- decompose.graph(g, mode = "weak", min.vertices = 3)[[1]]
l2 <- layout.fruchterman.reingold(sub, weights = E(sub)$weight)
par(mar=c(0,0,1,0))
plot(sub, edge.width = E(sub)$weight * 10, layout = l2,
     edge.arrow.size= 0.15, vertex.size = 5)
title("Largest family of codes")
```

Neighborhood of NY 1850

```{r}
ny <- which(V(g)$name == "NY1850")
neighbors(g, ny)
graph.neighborhood(g, order = 2, nodes = ny)[[1]] %>%
  plot_graph()
```
